A Summery about reasoning with logic

### 2015-10-27 reasoning/summery.tex
added the connectives

Then write down the lemmas you're gonna use. A lemma is a little proof, often
derived from the properties of the system you're proving. You could see it
as a basic argument. When proving soundness you want to connect this to the
semantics, for classical systems the semantics are truth tables, for kripke
models it are kripke frames. The semantics are the thing your talking about
in your logical system.
%I can see how I dind't understand all this crap the first time I saw it,
% its freaking packed with definitions, and even if you understand all the
% definiontions, its still hard
Make sure that you've proven the soundness of the axioms *and* of the rules
with help of the semantics.

@@

\section{Systems}
GKC, Gentzen sequent calculy.

>>>>

Then write down the lemmas you're gonna use. A lemma is a little proof, often
derived from the properties of the system you're proving. You could see it
as a basic argument. When proving soundness you want to connect this to the
semantics, for propositional systems the semantics are truth tables, for kripke
models it are kripke frames. The semantics are the thing your talking about
in your logical system.
%I can see how I dind't understand all this crap the first time I saw it,
% its freaking packed with definitions, and even if you understand all the
% definiontions, its still hard
Make sure that you've proven the soundness of the axioms *and* of the rules
with help of the semantics.

@@

\noindent
\begin{tabular}{@{}lll@{}}
Symbols&
In natural language &
Technical name \\ \toprule
$\neg$ 			& not 				& negation \\
$\wedge$,\& 	& and 				& conjunction \\
$\vee$ 			& or 				& disjunction\\
$\to$	& if \ldots then 	& implication\\
$\leftrightarrow$	& if and only if 	& equivalent\\ \bottomrule
\end{tabular}

Then there are some other symbols used:

\noindent
\begin{tabular}{@{}ll@{}}
Symbols&
In natural language \\ \toprule
$\vdash$ 					& Part of system \\
$\vdash, \Rightarrow$ 		& Seperator between antecedent and succedent\\ \bottomrule
\end{tabular}

\section{Systems}
\begin{itemize}
	\item $H$  Hilbert, has a huge set of axioms, and only 1 rule. (also called fredge)
	\item $CPC$ Clasicial Propositional logic, formulas in here are always true
(tautologies)
	\item $GKC$ Gentzen calculus, also called sequent calcules
	\item $GKC_K$  Getnzen + R 
\end{itemize}
